\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\A Three-Tier Architecture Visual-Programming Platform for Building-Lifecycle Data Management

### 2020-03-30 paper_LateX/main.tex
Updates from Overleaf

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/platform_interface.png}
\caption{The main interface functions}
\label{fig:platformInterface}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/tpl_interface.png}
\caption{TPL interface using Python script. The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs.}
\label{fig:tpl_interface}
\end{figure}
\subsection{Dashboard and forms}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/platform_interface.png}
\caption{The main interface functions -- a higher resolution image can be viewed \href{https://raw.githubusercontent.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform/master/paper_LateX/imgs/platform_interface.png}{here.}}
\label{fig:platformInterface}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/tpl_interface.png}
\caption{TPL interface using Python script. The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs -- a higher resolution image can be viewed \href{https://raw.githubusercontent.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform/master/paper_LateX/imgs/tpl_interface.png}{here}}
\label{fig:tpl_interface}
\end{figure}
\subsection{Dashboard and forms}
